Biotic interactions structure zooplankton metacommunity dynamics following a summer heatwave

### 2024-03-07 writing/Manuscript.Rmd
replace .RData file with csvs
add check for model file

```{r, loadData, echo=FALSE, include = FALSE}
load("../data/zoop_data.RData")
```

@@

#m <- sampleMcmc(m, thin = thin, samples = samples, transient = transient, nChains = 4, nParallel = 4)
#save(m, file = "../data/zooplankton/HMSC_m.RData")

load("../data/HMSC_m.RData")

>>>>

```{r, loadData, echo=FALSE, include = FALSE}
Zoop_data <- read.csv("../data/Zoop_data.csv")
all_temperature <- read.csv("../data/all_temperature.csv")
```

@@

if(file.exists("../data/HMSC_m.RData")){
  load("../data/HMSC_m.RData")
} else{
  m <- sampleMcmc(m, thin = thin, samples = samples, transient = transient, nChains = 4, nParallel = 4)
  save(m, file = "../data/zooplankton/HMSC_m.RData")
}
